Fast, Scalable Phrase-Based SMT Decoding

### 2016-05-06 acl.2016/acl2016.tex
changes

Jane and mtplz are single-threaded decoders, relying on external applications to parallelize operations. This has the advantage it is easier to parallelize processing across multiple servers, not just multiple cores. As we shall see, this method does not scale beyond a small number of cores when attempting to scale to multiple cores within one server.

@@

We mimic the use of multi-core servers by single-threaded decoders such as mtplz~\cite{Heafield-mtplz} and Jane~\cite{peitz2012jane} by running multiple processes of the Moses decoder, each running one thread. The input is distributed to the processes using a external script.

The results in ??? shows that not only does the parallelization method scales badly even compared to Moses, it is unable to run at all when more that a certain number of threads, possibly due to higher memory requirements of running multiple memory-hungry processes, or the inefficiency of distributing work to many processes. Based on this result, single-thread decoding applications are not a viable option for efficiently utilizing the multicore servers of today.

>>>>

Jane and mtplz are single-threaded decoders, relying on external applications to parallelize operations. %This has the advantage it is easier to parallelize processing across multiple servers, not just multiple cores. As we shall see, this method does not scale beyond a small number of cores when attempting to scale to multiple cores within one server.

@@

%We mimic the use of multi-core servers by single-threaded decoders such as mtplz~\cite{Heafield-mtplz} and Jane~\cite{peitz2012jane} by running multiple processes of the Moses decoder, each running one thread. The input is distributed to the processes using a external script. The result in Figure~\ref{fig:moses-speed} (dashed line) shows that this method scales much better than multithreading the application.
